---
title: "p8105_hw6_yc4384"
author: "Yangyang Chen"
date: "`r Sys.Date()`"
output: github_document
---
```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem_1
```{r library packages, echo=FALSE, results='hide', message=FALSE}
library(tidyverse)
```
This dataset records the crimes solved rate in each state - The Washington Post has gathered data on homicides in 50 large U.S. cities.

## _Data pre-processing_

* Add a character variable `city_state` representing `city` and `state` variables;

* Add a binary variable `resolved` to indicate whether cases were solved or not;

* Limit `victim_race` to `black` and `white` people;

* Filter cities `Tulsa, AL`, `Dallas, TX`, `Phoenix, AZ`, `Kansas City, MO` as they contain NA values;

* Drop NAs to guarantee `victim_age` is numeric.

```{r pre-processing, message=FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) |> 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolved = as.numeric(disposition == "Closed by arrest")
  ) |> 
  filter(victim_race %in% c("Black", "White"),
         !(city_state %in% c("Tulsa, AL", "Dallas, TX", "Phoenix, AZ", "Kansas City, MO"))) |> 
  drop_na() |> 
  select(resolved, victim_age, victim_race, victim_sex, city_state)
```

## _Fitting Models_
```{r}
fit_logistic = 
  homicide_df |> 
  filter(city_state == "Baltimore, MD") |> 
  glm(resolved ~ victim_age + victim_sex + victim_race, data = _, family = binomial()) |> 
  broom::tidy() |> 
  mutate(OR = exp(estimate)) |> 
  select(term, estimate, OR)
```


