---
title: "p8105_hw6_yc4384"
author: "Yangyang Chen"
date: "`r Sys.Date()`"
output: github_document
---
```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# _Problem_1_
```{r library packages, echo=FALSE, results='hide', message=FALSE}
library(tidyverse)
```
This dataset records the crimes solved rate in each state - The Washington Post has gathered data on homicides in 50 large U.S. cities.

## _Data pre-processing_

* Add a character variable `city_state` representing `city` and `state` variables;

* Add a binary variable `resolved` to indicate whether cases were solved or not;

* Limit `victim_race` to `black` and `white` people;

* Filter cities `Tulsa, AL`, `Dallas, TX`, `Phoenix, AZ`, `Kansas City, MO` as they contain NA values;

* Drop NAs to guarantee `victim_age` is numeric.

```{r pre-processing, message=FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) |> 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolved = as.numeric(disposition == "Closed by arrest")
  ) |> 
  filter(victim_race %in% c("Black", "White"),
         !(city_state %in% c("Tulsa, AL", "Dallas, TX", "Phoenix, AZ", "Kansas City, MO"))) |> 
  drop_na() |> 
  select(resolved, victim_age, victim_race, victim_sex, city_state)
```

## _Fitting Logistics Regression For Baltimore, MD_

I fitted a model using age, sex and race variables to compute odds ratio and confidence interval of solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
fit_logistic = 
  homicide_df |> 
  filter(city_state == "Baltimore, MD") |> 
  glm(resolved ~ victim_age + victim_sex + victim_race, data = _, family = binomial()) |>
  broom::tidy() |> 
  mutate(OR = exp(estimate),
         conf.low = exp(estimate - 1.96 * std.error),
         conf.high = exp(estimate + 1.96 * std.error)) |> 
  select(term, estimate, OR, starts_with("conf")) |> 
  knitr::kable(digits = 3)
fit_logistic
```

## _Fitting Logistics Regression For Each City_

Then I used `map` function to obtain each city's Adjusted Odds Ratio and CIs for solving homicides comparing male victims to female victims.

```{r}
city_logistic = 
  homicide_df |> 
  group_by(city_state)|> 
  nest(data = -city_state) |> 
  mutate(
    glm_logistics = map(.x = data, ~glm(resolved ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
    tidy_tests = map(glm_logistics, broom::tidy)) |>  #mapping
  unnest(tidy_tests) |> 
  mutate(
    OR = exp(estimate),
    conf.low = exp(estimate - 1.96 * std.error),
    conf.high = exp(estimate + 1.96 * std.error)
  ) |> #CI
  select(city_state, term, OR, starts_with("conf.")) |> # table labels
  mutate(city_state = fct_reorder(city_state, OR)) |> 
  filter(term == "victim_sexMale") 
  
city_logistic |> 
  head() |> 
  knitr::kable(digits = 3)

```

## Plotting for ORs and CIs in Each City

```{r}
city_logistic |> 
  mutate(city_state = fct_reorder(city_state, OR)) |> 
  ggplot(aes(x = OR, y = city_state)) +
  geom_point() +
  geom_errorbar(aes(xmax = conf.high, xmin = conf.low)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

From the above plot, we observed that Washington, DC has the lowest odds ratio, indicating the lowest resolved homicide cases; while Albuquerque, NM, has the highest odds ratio. Noticing that Fresno, CA has the widest confidence interval of OR among all cities, while Balttimore, MD has the narrowest confidence interval. Overall, there exists plenty of overlapping areas of CIs among all cities.


